Notes on Wide Gap

### 2016-05-18 paper/wide_gap_notes.tex
test contribution of nonlinear advective terms
still not at critical infl point

The nonlinear terms in the wide-gap case differ from their thin-gap analogues mainly in the addition of vertical advective terms. These terms derive from the advective derivatives in the momentum and induction equations, but are filtered out in the thin-gap approximation. These terms have several interesting consequences. First, they allow the nonlinear contributions at both second and third order (i.e. N$_2$ and N$_3$) not to individually satisfy the boundary conditions on $\Psi$ and $u$. Second, the advection terms break the alternating parity exhibited by the thin-gap nonlinear terms.

>>>>

The nonlinear terms in the wide-gap case differ from their thin-gap analogues mainly in the addition of vertical advective terms. These terms derive from the advective derivatives in the momentum and induction equations, but are filtered out in the thin-gap approximation. These terms have several interesting consequences. First, they allow the nonlinear contributions at both second and third order (i.e. N$_2$ and N$_3$) not to individually satisfy the boundary conditions on $\Psi$ and $u$.

The astrophysical magnetorotational instability operates in accretion disks and in stellar interiors. In accretion disks, differential rotation is imposed gravitationally by a central body. In a Taylor-Couette flow, differential rotation is created by rotating an inner cylinder faster than an outer cylinder. In a non ideal fluid

-- MRI mode can be conceptualized as a quantum mechanical particle in a box
-- In the ideal thin-gap case, V = constant, and thus invariant under parity. Walls and boundary conditions impose symmetric and antisymmetric states.
-- In the ideal wide-gap case, V is a function of r
-- I expect the coefficients of the GLE to be complex in the wide-gap case..

%Second, the advection terms break the alternating parity exhibited by the thin-gap nonlinear terms. % no they don't
